---
title: "Automation-Job Quality Regression Output"
output: pdf_document
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(foreign)
library(dplyr)
library(reshape2)
library(naniar)
library(ggplot2)
library(plm)
#https://cran.r-project.org/web/packages/outreg/outreg.pdf
#https://github.com/kota7/outreg/blob/master/README.md
library(outreg)
library(texreg)
library(stargazer)
```

```{r, echo=FALSE}
setwd("/Volumes/LARRYLIU/iclouddrive/Automation Work Project")
##Load gss9.csv
gss9<-read.csv("gss9.csv")

##create new variable: Capital labor ratio with top 5 percentiles cut out
kl_ratio95<-gss9[gss9$kl_ratio<quantile(gss9$kl_ratio,0.95, na.rm=TRUE),]
kl_ratio95<-select(kl_ratio95, X, kl_ratio)
kl_ratio95<-rename(kl_ratio95, kl_ratio95=kl_ratio)
gss9<-merge(gss9, kl_ratio95, by='X', all.x=TRUE)
```

#Regression Models

##Explanatory Variables: Automation

1.Computerization Probability (Frey and Osborne 2013)

2.Percentile software/100 (Webb 2020)

3.Percentile robot/100 (Webb 2020)

4.Percentile AI/100 (Webb 2020)

5.Capital-Output Ratio (World KLEMS)

6.Capital-Labor Ratio (World KLEMS)

7.Declining Job Outlook (O*Net): (a) Binary (1: Declining, 0: All Other), (b) Ordinal (5: Declining, 4: Little or no Change, 3: Slower than Average, 2: Average, 1: Faster than Average, 0: Much faster than Average)

##Dependent Variables: Job Quality

1.Stress: How often does r find work stressful; (a) dichotomous, StressD (0: "Never", "Hardly ever", "Sometimes", 1: "Often", "Always"), (b) ordinal, StressN (0: "Never", 1: "Hardly ever", 2: "Sometimes", 3: "Often", 4: "Always")

2.Job Satisafaction: Job satisfaction in general; (a) dichotomous, JobSatD (0:"Not at all satisfied", "Not too satisfied", 1: "Somewhat satisfied", "Very satisfied"), (b) ordinal, JobSatN (0:"Not at all satisfied", 1:"Not too satisfied", 2:"Somewhat satisfied", 3:"Very satisfied")

3: Self-rated Health: Rs health in general; (a) dichotomous, HealthD (0: "Poor", 1: "Fair", "Good", "Very good", "Excellent"), (b) ordinal, HealthN (0: "Poor", 1: "Fair", 2:"Good", 3:"Very good", 4:"Excellent")

4: Job Security: The job security is good; (a) dichotomous, JobSecD (0:"Not at all true", "Not too true", 1: "Somewhat true", "Very true"), ordinal, JobSecN (0:"Not at all true", 1:"Not too true", 2:"Somewhat true", 3:"Very true")

5: Fringe benefits are good; (a) dichotomous, FringeD (0:"Not at all true", "Not too true", 1: "Somewhat true", "Very true"), (b) ordinal, FringeN (0:"Not at all true", 1:"Not too true", 2:"Somewhat true", 3:"Very true")

6: Second Job: R has job other than main; dichotomous, SecJobD (0:"No", 1:"Yes")

7:Family Leave: How hard to take time off; (a) dichotomous, TimeOffD (0: "Very hard", "Somewhat hard", 1: "Not too hard", "Not at all hard"), (b) ordinal, TimeOffN (0: "Very hard", 1:"Somewhat hard", 2:"Not too hard", 3:"Not at all hard")

8:Full-time work: Was r's work part-time or full-time?, dichotomous, FullD (0: "Part-time", 1: "Full-time")

##Models

OLS for ordinal dependent variables. Logistic regression for dichotomous dependent variables.

Table 1: Descriptive Statistics

Table 2 and 3: Computerization and Job Quality 

Table 4 and 5: Computerization and Job Quality, Year Interaction

Table 6 and 7: Webb-Software Percentile and Job Quality

Table 8 and 9: Webb-Software Percentile and Job Quality, Year Interaction

Table 10 and 11: Webb-Robot Percentile and Job Quality

Table 12 and 13: Webb-Robot Percentile and Job Quality, Year Interaction

Table 14 and 15: Webb-AI Percentile and Job Quality

Table 16 and 17: Webb-AI Percentile and Job Quality, Year Interaction

Table 18 and 19: Capital-Output Ratio and Job Quality

Table 20 and 21: Capital-Output Ratio and Job Quality, Year Interaction

Table 22 and 23: Capital-Labor Ratio and Job Quality

Table 24 and 25: Capital-Labor Ratio and Job Quality, Year Interaction

Table 26 and 27: Declining Job Outlook Binary and Job Quality

Table 28 and 29: Declining Job Outlook Binary and Job Quality, Year Interaction

Table 30 and 31: Declining Job Outlook Ordinal and Job Quality

Table 32 and 33: Declining Job Outlook Ordinal and Job Quality, Year Interaction

```{r, echo=FALSE}
descriptive<-select(gss9, stressn, satjob1n, health1n, jobsecokn,
                    fringeokn, secondwkd, famwkoffn, fulld, rincomed,
                    blackraced, femalesexd, colleged, computefrey,
                    pct_software, pct_robot, pct_ai, ko_ratio, 
                    kl_ratio95, declineord)
colnames(descriptive)<-c("Stress", "Job Satisfaction", "Self-rated health",
                         "Job Security", "Good Fringe Benefits",
                         "Have Second Job", "Can take Family Leave",
                         "Full-time Work", "Income above $25K",
                         "Black", "Female", "4Y College", 
                         "Computerization Probability", 
                         "Percentile Software", "Percentile Robot",
                         "Percentile AI", "Capital-Output Ratio",
                         "Capital-Labor Ratio", "Declining Job Outlook")
```

```{r, results='asis', echo=FALSE}
##Table 1: 
stargazer(as.data.frame(descriptive), title="Descriptive statistics",
          type="html", digits=2, omit.summary.stat=c("p25", "p75"), 
          header=FALSE, out="descriptive.doc")
```

```{r, echo=FALSE}
##Base
computestressd<-glm(stressd~computefrey+rincomed+blackraced+
                    femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
computestressn<-lm(stressn~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
computesatjob1d<-glm(satjob1d~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                     family=binomial(link="logit"))
computesatjob1n<-lm(satjob1n~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
computehealth1d<-glm(health1d~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
computehealth1n<-lm(health1n~computefrey+rincomed+blackraced+
                     femalesexd+colleged, data=gss9)
computejobsecokd<-glm(jobsecokd~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
computejobsecokn<-lm(jobsecokn~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
computefringeokd<-glm(fringeokd~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
computefringeokn<-lm(fringeokn~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
computesecondwkd<-glm(secondwkd~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
computefamwkoffd<-glm(famwkoffd~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
computefamwkoffn<-lm(famwkoffn~computefrey+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
ycomputestressd<-glm(stressd~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputestressn<-lm(stressn~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ycomputesatjob1d<-glm(satjob1d~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputesatjob1n<-lm(satjob1n~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ycomputehealth1d<-glm(health1d~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputehealth1n<-lm(health1n~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ycomputejobsecokd<-glm(jobsecokd~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputejobsecokn<-lm(jobsecokn~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ycomputefringeokd<-glm(fringeokd~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputefringeokn<-lm(fringeokn~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ycomputesecondwkd<-glm(secondwkd~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputefamwkoffd<-glm(famwkoffd~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ycomputefamwkoffn<-lm(famwkoffn~computefrey*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base
softwarestressd<-glm(stressd~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwarestressn<-lm(stressn~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
softwaresatjob1d<-glm(satjob1d~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwaresatjob1n<-lm(satjob1n~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
softwarehealth1d<-glm(health1d~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwarehealth1n<-lm(health1n~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
softwarejobsecokd<-glm(jobsecokd~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwarejobsecokn<-lm(jobsecokn~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
softwarefringeokd<-glm(fringeokd~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwarefringeokn<-lm(fringeokn~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
softwaresecondwkd<-glm(secondwkd~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwarefamwkoffd<-glm(famwkoffd~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
softwarefamwkoffn<-lm(famwkoffn~pct_software+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
ysoftwarestressd<-glm(stressd~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwarestressn<-lm(stressn~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ysoftwaresatjob1d<-glm(satjob1d~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwaresatjob1n<-lm(satjob1n~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ysoftwarehealth1d<-glm(health1d~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwarehealth1n<-lm(health1n~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ysoftwarejobsecokd<-glm(jobsecokd~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwarejobsecokn<-lm(jobsecokn~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ysoftwarefringeokd<-glm(fringeokd~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwarefringeokn<-lm(fringeokn~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ysoftwaresecondwkd<-glm(secondwkd~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwarefamwkoffd<-glm(famwkoffd~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ysoftwarefamwkoffn<-lm(famwkoffn~pct_software*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base
robotstressd<-glm(stressd~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robotstressn<-lm(stressn~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
robotsatjob1d<-glm(satjob1d~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robotsatjob1n<-lm(satjob1n~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
robothealth1d<-glm(health1d~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robothealth1n<-lm(health1n~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
robotjobsecokd<-glm(jobsecokd~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robotjobsecokn<-lm(jobsecokn~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
robotfringeokd<-glm(fringeokd~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robotfringeokn<-lm(fringeokn~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
robotsecondwkd<-glm(secondwkd~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robotfamwkoffd<-glm(famwkoffd~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
robotfamwkoffn<-lm(famwkoffn~pct_robot+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
yrobotstressd<-glm(stressd~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobotstressn<-lm(stressn~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yrobotsatjob1d<-glm(satjob1d~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobotsatjob1n<-lm(satjob1n~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yrobothealth1d<-glm(health1d~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobothealth1n<-lm(health1n~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yrobotjobsecokd<-glm(jobsecokd~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobotjobsecokn<-lm(jobsecokn~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yrobotfringeokd<-glm(fringeokd~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobotfringeokn<-lm(fringeokn~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yrobotsecondwkd<-glm(secondwkd~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobotfamwkoffd<-glm(famwkoffd~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yrobotfamwkoffn<-lm(famwkoffn~pct_robot*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base
aistressd<-glm(stressd~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aistressn<-lm(stressn~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
aisatjob1d<-glm(satjob1d~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aisatjob1n<-lm(satjob1n~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
aihealth1d<-glm(health1d~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aihealth1n<-lm(health1n~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
aijobsecokd<-glm(jobsecokd~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aijobsecokn<-lm(jobsecokn~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
aifringeokd<-glm(fringeokd~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aifringeokn<-lm(fringeokn~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
aisecondwkd<-glm(secondwkd~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aifamwkoffd<-glm(famwkoffd~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
aifamwkoffn<-lm(famwkoffn~pct_ai+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
yaistressd<-glm(stressd~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaistressn<-lm(stressn~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yaisatjob1d<-glm(satjob1d~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaisatjob1n<-lm(satjob1n~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yaihealth1d<-glm(health1d~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaihealth1n<-lm(health1n~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yaijobsecokd<-glm(jobsecokd~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaijobsecokn<-lm(jobsecokn~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yaifringeokd<-glm(fringeokd~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaifringeokn<-lm(fringeokn~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yaisecondwkd<-glm(secondwkd~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaifamwkoffd<-glm(famwkoffd~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yaifamwkoffn<-lm(famwkoffn~pct_ai*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base
kostressd<-glm(stressd~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kostressn<-lm(stressn~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
kosatjob1d<-glm(satjob1d~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kosatjob1n<-lm(satjob1n~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
kohealth1d<-glm(health1d~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kohealth1n<-lm(health1n~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
kojobsecokd<-glm(jobsecokd~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kojobsecokn<-lm(jobsecokn~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
kofringeokd<-glm(fringeokd~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kofringeokn<-lm(fringeokn~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
kosecondwkd<-glm(secondwkd~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kofamwkoffd<-glm(famwkoffd~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kofamwkoffn<-lm(famwkoffn~ko_ratio+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
ykostressd<-glm(stressd~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykostressn<-lm(stressn~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykosatjob1d<-glm(satjob1d~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykosatjob1n<-lm(satjob1n~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykohealth1d<-glm(health1d~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykohealth1n<-lm(health1n~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykojobsecokd<-lm(jobsecokd~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykojobsecokn<-lm(jobsecokn~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykofringeokd<-glm(fringeokd~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykofringeokn<-lm(fringeokn~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykosecondwkd<-glm(secondwkd~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykofamwkoffd<-glm(famwkoffd~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykofamwkoffn<-lm(famwkoffn~ko_ratio*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base: Capital-Labor Ratio
klstressd<-glm(stressd~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
klstressn<-lm(stressn~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
klsatjob1d<-glm(satjob1d~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
klsatjob1n<-lm(satjob1n~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
klhealth1d<-glm(health1d~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
klhealth1n<-lm(health1n~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
kljobsecokd<-glm(jobsecokd~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
kljobsecokn<-lm(jobsecokn~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
klfringeokd<-glm(fringeokd~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
klfringeokn<-lm(fringeokn~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
klsecondwkd<-glm(secondwkd~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
klfamwkoffd<-glm(famwkoffd~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
klfamwkoffn<-lm(famwkoffn~kl_ratio95+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
yklstressd<-glm(stressd~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yklstressn<-lm(stressn~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yklsatjob1d<-glm(satjob1d~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yklsatjob1n<-lm(satjob1n~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yklhealth1d<-glm(health1d~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yklhealth1n<-lm(health1n~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ykljobsecokd<-glm(jobsecokd~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ykljobsecokn<-lm(jobsecokn~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yklfringeokd<-glm(fringeokd~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yklfringeokn<-lm(fringeokn~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
yklsecondwkd<-glm(secondwkd~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yklfamwkoffd<-glm(famwkoffd~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
yklfamwkoffn<-lm(famwkoffn~kl_ratio95*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base
declinestressd<-glm(stressd~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinestressn<-lm(stressn~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declinesatjob1d<-glm(satjob1d~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinesatjob1n<-lm(satjob1n~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declinehealth1d<-glm(health1d~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinehealth1n<-lm(health1n~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declinejobsecokd<-glm(jobsecokd~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinejobsecokn<-lm(jobsecokn~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declinefringeokd<-glm(fringeokd~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinefringeokn<-lm(fringeokn~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declinesecondwkd<-glm(secondwkd~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinefamwkoffd<-glm(famwkoffd~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declinefamwkoffn<-lm(famwkoffn~decline+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
ydeclinestressd<-glm(stressd~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinestressn<-lm(stressn~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclinesatjob1d<-glm(satjob1d~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinesatjob1n<-lm(satjob1n~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclinehealth1d<-glm(health1d~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinehealth1n<-lm(health1n~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclinejobsecokd<-glm(jobsecokd~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinejobsecokn<-lm(jobsecokn~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclinefringeokd<-glm(fringeokd~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinefringeokn<-lm(fringeokn~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclinesecondwkd<-glm(secondwkd~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinefamwkoffd<-glm(famwkoffd~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclinefamwkoffn<-lm(famwkoffn~decline*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##Base
declineordstressd<-glm(stressd~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordstressn<-lm(stressn~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declineordsatjob1d<-glm(satjob1d~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordsatjob1n<-lm(satjob1n~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declineordhealth1d<-glm(health1d~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordhealth1n<-lm(health1n~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declineordjobsecokd<-glm(jobsecokd~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordjobsecokn<-lm(jobsecokn~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declineordfringeokd<-glm(fringeokd~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordfringeokn<-lm(fringeokn~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
declineordsecondwkd<-glm(secondwkd~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordfamwkoffd<-glm(famwkoffd~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
declineordfamwkoffn<-lm(famwkoffn~declineord+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)

##Year Interaction
ydeclineordstressd<-glm(stressd~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordstressn<-lm(stressn~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclineordsatjob1d<-glm(satjob1d~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordsatjob1n<-lm(satjob1n~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclineordhealth1d<-glm(health1d~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordhealth1n<-lm(health1n~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclineordjobsecokd<-glm(jobsecokd~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordjobsecokn<-lm(jobsecokn~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclineordfringeokd<-glm(fringeokd~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordfringeokn<-lm(fringeokn~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
ydeclineordsecondwkd<-glm(secondwkd~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordfamwkoffd<-glm(famwkoffd~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9, 
                    family=binomial(link="logit"))
ydeclineordfamwkoffn<-lm(famwkoffn~declineord*year+rincomed+blackraced+
                     femalesexd+colleged+fulld, data=gss9)
```

```{r, echo=FALSE}
##create list of regression
##Base Computerization, Frey-Osborne
computelist1<-list(computestressd,
                  computestressn,
                  computesatjob1d,
                  computesatjob1n,
                  computehealth1d,
                  computehealth1n,
                  computejobsecokd)

computelist2<-list(computejobsecokn,
                  computefringeokd,
                  computefringeokn,
                  computesecondwkd,
                  computefamwkoffd,
                  computefamwkoffn)

##Year-Interaction, Computerization
ycomputelist1<-list(ycomputestressd,
                    ycomputestressn,
                    ycomputesatjob1d,
                    ycomputesatjob1n,
                    ycomputehealth1d,
                    ycomputehealth1n,
                    ycomputejobsecokd)
ycomputelist2<-list(ycomputejobsecokn,
                    ycomputefringeokd,
                    ycomputefringeokn,
                    ycomputesecondwkd,
                    ycomputefamwkoffd,
                    ycomputefamwkoffn)

##Base Webb-Software
softwarelist1<-list(softwarestressd,
                  softwarestressn,
                  softwaresatjob1d,
                  softwaresatjob1n,
                  softwarehealth1d,
                  softwarehealth1n,
                  softwarejobsecokd)

softwarelist2<-list(softwarejobsecokn,
                  softwarefringeokd,
                  softwarefringeokn,
                  softwaresecondwkd,
                  softwarefamwkoffd,
                  softwarefamwkoffn)

##Year-Interaction, Webb-Software
ysoftwarelist1<-list(ysoftwarestressd,
                    ysoftwarestressn,
                    ysoftwaresatjob1d,
                    ysoftwaresatjob1n,
                    ysoftwarehealth1d,
                    ysoftwarehealth1n,
                    ysoftwarejobsecokd)
ysoftwarelist2<-list(ysoftwarejobsecokn,
                    ysoftwarefringeokd,
                    ysoftwarefringeokn,
                    ysoftwaresecondwkd,
                    ysoftwarefamwkoffd,
                    ysoftwarefamwkoffn)

##Base Robots-Webb
robotlist1<-list(robotstressd,
                  robotstressn,
                  robotsatjob1d,
                  robotsatjob1n,
                  robothealth1d,
                  robothealth1n,
                  robotjobsecokd)

robotlist2<-list(robotjobsecokn,
                  robotfringeokd,
                  robotfringeokn,
                  robotsecondwkd,
                  robotfamwkoffd,
                  robotfamwkoffn)

##Year-Interaction, Robots-Webb
yrobotlist1<-list(yrobotstressd,
                    yrobotstressn,
                    yrobotsatjob1d,
                    yrobotsatjob1n,
                    yrobothealth1d,
                    yrobothealth1n,
                    yrobotjobsecokd)
yrobotlist2<-list(yrobotjobsecokn,
                    yrobotfringeokd,
                    yrobotfringeokn,
                    yrobotsecondwkd,
                    yrobotfamwkoffd,
                    yrobotfamwkoffn)

##Base AI-Webb
ailist1<-list(aistressd,
                  aistressn,
                  aisatjob1d,
                  aisatjob1n,
                  aihealth1d,
                  aihealth1n,
                  aijobsecokd)

ailist2<-list(aijobsecokn,
                  aifringeokd,
                  aifringeokn,
                  aisecondwkd,
                  aifamwkoffd,
                  aifamwkoffn)

##Year-Interaction, AI-Webb
yailist1<-list(yaistressd,
                    yaistressn,
                    yaisatjob1d,
                    yaisatjob1n,
                    yaihealth1d,
                    yaihealth1n,
                    yaijobsecokd)
yailist2<-list(yaijobsecokn,
                    yaifringeokd,
                    yaifringeokn,
                    yaisecondwkd,
                    yaifamwkoffd,
                    yaifamwkoffn)

##Base KO-ratio
kolist1<-list(kostressd,
                  kostressn,
                  kosatjob1d,
                  kosatjob1n,
                  kohealth1d,
                  kohealth1n,
                  kojobsecokd)

kolist2<-list(kojobsecokn,
                  kofringeokd,
                  kofringeokn,
                  kosecondwkd,
                  kofamwkoffd,
                  kofamwkoffn)

##Year-Interaction, KO-Ratio
ykolist1<-list(ykostressd,
                    ykostressn,
                    ykosatjob1d,
                    ykosatjob1n,
                    ykohealth1d,
                    ykohealth1n,
                    ykojobsecokd)
ykolist2<-list(ykojobsecokn,
                    ykofringeokd,
                    ykofringeokn,
                    ykosecondwkd,
                    ykofamwkoffd,
                    ykofamwkoffn)

##Base, KL-Ratio
kllist1<-list(klstressd,
                  klstressn,
                  klsatjob1d,
                  klsatjob1n,
                  klhealth1d,
                  klhealth1n,
                  kljobsecokd)

kllist2<-list(kljobsecokn,
                  klfringeokd,
                  klfringeokn,
                  klsecondwkd,
                  klfamwkoffd,
                  klfamwkoffn)

##Year-Interaction, Computerization
ykllist1<-list(yklstressd,
                    yklstressn,
                    yklsatjob1d,
                    yklsatjob1n,
                    yklhealth1d,
                    yklhealth1n,
                    ykljobsecokd)
ykllist2<-list(ykljobsecokn,
                    yklfringeokd,
                    yklfringeokn,
                    yklsecondwkd,
                    yklfamwkoffd,
                    yklfamwkoffn)

##Base Declining Outlook
declinelist1<-list(declinestressd,
                  declinestressn,
                  declinesatjob1d,
                  declinesatjob1n,
                  declinehealth1d,
                  declinehealth1n,
                  declinejobsecokd)

declinelist2<-list(declinejobsecokn,
                  declinefringeokd,
                  declinefringeokn,
                  declinesecondwkd,
                  declinefamwkoffd,
                  declinefamwkoffn)

##Year-Interaction, Declining Job Outlook
ydeclinelist1<-list(ydeclinestressd,
                    ydeclinestressn,
                    ydeclinesatjob1d,
                    ydeclinesatjob1n,
                    ydeclinehealth1d,
                    ydeclinehealth1n,
                    ydeclinejobsecokd)
ydeclinelist2<-list(ydeclinejobsecokn,
                    ydeclinefringeokd,
                    ydeclinefringeokn,
                    ydeclinesecondwkd,
                    ydeclinefamwkoffd,
                    ydeclinefamwkoffn)

##Base, Decline ordinal
declineordlist1<-list(declineordstressd,
                  declineordstressn,
                  declineordsatjob1d,
                  declineordsatjob1n,
                  declineordhealth1d,
                  declineordhealth1n,
                  declineordjobsecokd)

declineordlist2<-list(declineordjobsecokn,
                  declineordfringeokd,
                  declineordfringeokn,
                  declineordsecondwkd,
                  declineordfamwkoffd,
                  declineordfamwkoffn)

##Year-Interaction, Computerization
ydeclineordlist1<-list(ydeclineordstressd,
                    ydeclineordstressn,
                    ydeclineordsatjob1d,
                    ydeclineordsatjob1n,
                    ydeclineordhealth1d,
                    ydeclineordhealth1n,
                    ydeclineordjobsecokd)
ydeclineordlist2<-list(ydeclineordjobsecokn,
                    ydeclineordfringeokd,
                    ydeclineordfringeokn,
                    ydeclineordsecondwkd,
                    ydeclineordfamwkoffd,
                    ydeclineordfamwkoffn)
```


```{r, echo=FALSE, results='asis'}
##Computerization, Frey-Osborne
wordreg(computelist1,
        file="computelist1.doc",
       caption="Computerization and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Computerization Prob",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(computelist2,
        file="computelist2.doc",
       caption="Computerization and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Computerization Prob",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(ycomputelist1,
       caption="Year Interaction, Computerization and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Computerization Prob", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Compute x 2010",
                             "Compute x 2018"))
texreg(ycomputelist2,
       caption="Year Interaction, Computerization and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Computerization Prob", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Compute x 2010",
                             "Compute x 2018"))

##Webb-Software
wordreg(softwarelist1,
       file="softwarelist1.doc",
       caption="Webb-Software Percentile and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "WebbSoftwarePct",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(softwarelist2,
        file="softwarelist2.doc",
       caption="Webb-Software Percentile and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "WebbSoftwarePct",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(ysoftwarelist1,
       caption="Year Interaction, Webb-Software Percentile and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "WebbSoftwarePct", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Software Pct x 2010",
                             "Software Pct x 2018"))
texreg(ysoftwarelist2,
       caption="Year Interaction, Webb-Software Percentile and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "WebbSoftwarePct", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Software Pct x 2010",
                             "Software Pct x 2018"))

##Webb-Robot
wordreg(robotlist1,
        file="robotlist1.doc",
       caption="Webb-Robot Percentile and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "WebbRobotPct",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(robotlist2,
        file="robotlist2.doc",
       caption="Webb-Robot Percentile and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "WebbRobotPct",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(yrobotlist1,
       caption="Year Interaction, Webb-Robot Percentile and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "WebbRobotPct", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Robot Pct x 2010",
                             "Robot Pct x 2018"))
texreg(yrobotlist2,
       caption="Year Interaction, Webb-Robot Percentile and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "WebbRobotPct", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Robot Pct x 2010",
                             "Robot Pct x 2018"))

##Webb-AI
wordreg(ailist1,
        file="ailist1.doc",
       caption="Webb-AI Percentile and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "WebbAI Pct",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(ailist2,
        file="ailist2.doc",
       caption="Webb-AI Percentile and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "WebbAI Pct",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(yailist1,
       caption="Year Interaction, Webb-AI Percentile and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "WebbAIPct", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "AI Pct x 2010",
                             "AI Pct x 2018"))
texreg(yailist2,
       caption="Year Interaction, Webb-AI Percentile and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "WebbAIPct", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "AI Pct x 2010",
                             "AI Pct x 2018"))

##KO-Ratio
wordreg(kolist1,
        file="kolist1.doc",
       caption="Capital-Output Ratio and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Capital-Output Ratio",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(kolist2,
        file="kolist2.doc",
       caption="Capital-Output Ratio and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Capital-Output Ratio",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(ykolist1,
       caption="Year Interaction, Capital-Output Ratio and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Capital-Output Ratio", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work",
                             "Capital-Output x 2010",
                             "Capital-Output x 2018"))
texreg(ykolist2,
       caption="Year Interaction, Capital-Output Ratio and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Capital-Output Ratio", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work",
                             "Capital-Output x 2010",
                             "Capital-Output x 2018"))

##KL-Ratio
wordreg(kllist1,
        file="kllist1.doc",
       caption="Capital-Labor Ratio and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Capital-Labor Ratio",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(kllist2,
        file="kllist2.doc",
       caption="Capital-Labor Ratio and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Capital-Labor Ratio",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(ykllist1,
       caption="Year Interaction, Capital-Labor Ratio and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Capital-Labor Ratio", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work",
                             "Capital-Labor x 2010",
                             "Capital-Labor x 2018"))
texreg(ykllist2,
       caption="Year Interaction, Capital-Labor Ratio and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Capital-Labor Ratio", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work",
                             "Capital-Labor x 2010",
                             "Capital-Labor x 2018"))

##Declining Job Outlook
wordreg(declinelist1,
        file="declinelist1.doc",
       caption="Declining Job Outlook Binary and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Declining Outlook, Binary",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(declinelist2,
        file="declinelist2.doc",
       caption="Declining Job Outlook Binary and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Declining Outlook, Binary",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(ydeclinelist1,
       caption="Year Interaction, Declining Job Outlook Binary and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Declining Outlook, Binary", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Declining x 2010",
                             "Declining x 2018"))
texreg(ydeclinelist2,
       caption="Year Interaction, Declining Job Outlook Binary and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Declining Outlook, Binary", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Declining x 2010",
                             "Declining x 2018"))

##Declining Job Outlook, Ordinal
wordreg(declineordlist1,
        file="declineordlist1.doc",
       caption="Declining Job Outlook Ordinal and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Declining Outlook, Ordinal",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))
wordreg(declineordlist2,
        file="declineordlist2.doc",
       caption="Declining Job Outlook Ordinal and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Declining Outlook, Ordinal",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work"))

texreg(ydeclineordlist1,
       caption="Year Interaction, Declining Job Outlook Ordinal and Job Quality",
       custom.model.names=c("StressD", "StressN", "JobSatD", "JobSatN",
                     "HealthD", "HealthN", "JobSecD"),
       custom.coef.names = c("Intercept", "Declining Outlook, Ordinal", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Declining x 2010",
                             "Declining x 2018"))
texreg(ydeclineordlist2,
       caption="Year Interaction, Declining Job Outlook Ordinal and Job Quality",
       custom.model.names=c("JobSecN", "FringeD", "FringeN", "SecJobD",
                     "TimeOffD", "TimeOffN"),
       custom.coef.names = c("Intercept", "Declining Outlook, Ordinal", 
                             "Year2010", "Year2018",
                             "Income", "Black", "Female", 
                             "College degree", "Full-time work", 
                             "Declining x 2010",
                             "Declining x 2018"))
```